\section{General}\label{index_main_general}
Iris is a simple network simulator for on-chip networks. It is developed at the Computer Architecture and Systems Laboratory, Georgia Institute of Technology.

\par
 Iris uses the Discrete Event Simulation methodology. Some of the models it provides: \begin{itemize}
\item An on chip memory controller model with supporting DDR2 and DDR3 delay models \item Switch Arbitor Models \item Routing Techniques \end{itemize}


Topologies Supported: \begin{itemize}
\item \doxyref{Mesh}{p.}{classMesh} $<$$>$

Getting Started: 1. These are the steps to compile the simulator \begin{itemize}
\item ./configure \item make \end{itemize}


2. Running the simulator: The simulator takes a configuration file. A sample config is in the config folder [config/generic.cfg]. Some of the configuration parameters may also be passed at the command line. Some of these options are listed here and others are documented in detail in the sample config file. ./simMc2Mesh config/generic.cfg

\begin{itemize}
\item for varying address mapping The bit positions of the address to be used to select the \doxyref{MC}{p.}{classMC} id can be specified at command line with switch --mc\_\-bits [eg. --mc\_\-bits 10] For distributing the address space among threads. The command line switch --thread\_\-id\_\-bits may be used\end{itemize}


-routing algorithms Various routing algorithms may be selected at command line with the switch --routing\_\-scheme [Eg. --routing\_\-scheme xy]

-switch arbitration Various switch arbitration schemes may be selected at command line with the switch --sw\_\-arbitration [Eg, --sw\_\-arbitration round-robin]

Switches may be added. For examples on how to add switches and use them follow the code in source/frontend/impl/simMc2Mesh.cc

Environment details: -------------------

The current version has been tested with 1. gcc version 4.3.3 (Ubuntu 4.3.3-5ubuntu4) Linux 2.6.28-18-generic \#60-Ubuntu SMP i686 GNU/Linux 2. gcc version 4.2.4 (Ubuntu 4.2.4-1ubuntu4) Linux 2.6.24-23-generic \#1 SMP i686 GNU/Linux \end{itemize}
\section{License}\label{index_main_license}
License??\section{Author}\label{index_Author}
Syed Minhaj Hassan. Mitchelle Rasquinha. {\tt }